---
output: pdf_document
---

__Mauro Lepore__

```{r, child="contact.Rmd"}
```
```{r, child="social.Rmd"}
```

---

__Tonya Filz__, Manager - Customer Success Team, RStudio  

Dear Tonya Filz and RStudio team,

Your open position for a [Customer Success Representative](https://hire.withgoogle.com/public/jobs/rstudiocom/view/P_AAAAAACAAJZPJ1EPP3oDOq) seems like an excellent opportunity for me to contribute to the growth and profit of RStudio. You have greatly contributed to my own growth. Now I would love to multiply the effect and help your customers be also wildly successful.

What you are looking for seems to match well with my skills and expertise:

* I learned to build trusted relationships and a deep understanding of my customers' needs during the many years I worked as a wedding photographer. It takes a lot of trust for a couple to decide who will preserve the memories of one of the most important moments of their lives. And I truly enjoy sharing insights and resources, which I hope is clear from my long experience teaching at multiple levels. I particularly like sharing RStudio resources. I do it frequently in my job, as an instructor of The Carpentries, as a guest of weekly meetings organized by ixpantia (one of your customers), and as a member of the R community in general.

* I have several years of experience selling photography, two years of experience as an R developer and consultant, and many accumulated year of experience as a trainer and teacher for learners of all levels, from primary school to professional researchers. Also I have plenty experience as a problem-solver. I solved human, logistic, and technical problems as a photographer; I solved conceptual, statistical, and communication problems as a researcher; and now I solve programming and data science problems as a package developer and consultant.

* My interest in statistics and data science is profound. I heavily used statistics during my PhD and postdoctoral work in ecology, and I am interested in data science far beyond my paid work. I continuously engage in opportunities to grow my data science skills and network. For example (thanks to an academic discount and a diversity scholarship from RStudio), I have attended the workshops "Building Tidy Tools" (2018) and "What They Forgot" (2019) and the most recent RStudio conference (2019). I have also attended multiple R-Ladies meetups, LatinR in Argentina (2018), rOpenSci's runconf 2018, and, chirunconf 2019. This should also demonstrate that my background in R programming is strong.

* I fully embrace continuous learning. I am most curious about data science, software engineering and human behavior. I read about one of these topics almost everyday.

* Multiple times in life I have gone way beyond my comfort zone and felt like an impostor. This has been extremely humbling. Some clear examples include living in different countries, doing a PhD in a foreign language, and dramatically changing careers. I believe in continuous improvement, so I will always consider myself a "work in progress". I love team work and I look forward to collaborating with others regularly. The most powerful and gratifying experiences I have had working in teams and asking for help were during the many years I worked as a life guard  -- I know this is cliche, but also very true.

* I am very effective working in a distributed team. Although I now work mostly from an office, the people I interact with are almost always elsewhere. In fact, the deepest, most productive work  I do everyday is from my home, during the first hour of my day and before I go to the office.

Please find my resume attached. I would appreciate the opportunity to meet with you and further discuss how I can help your team meet its goals.

Sincerely,  
Mauro Lepore  
